Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-03-06 paper/gloaguenAppliedNMF.tex
correct minor errors

where $\mathbf{w}$ is a $k$ element of $\mathbf{W}$ of $F \times 1$ dimension. When $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$=1, the element $k$ from $\mathbf{W'}$ is exactly similar than in $\mathbf{W_0}$. If $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$=0, the element is fully different. Next, the similarities are sorted in descending order. The extraction of traffic elements in $\mathbf{W'}$ is carried out by a hard thresholding method \cite{donoho1994threshold}. It consists in weigthing in a binary way the traffic elements $\mathbf{W'}$ according to $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$ and a threshold value such as :

@@

These methods are applied on simulated sound scenes in order to compare the estimated sound levels with the exact solutions. In \cite{}, the sound corpus was composed of a mix of traffic samples with specific sound classes (\textit{alert, animals, climate, human, mechanics, transportation}. Here, in order to implement this method in embedded sensors, a new more realistic sound corpus is generated based on urban recordings mixing all kind of sound sources.

@@

To transcribe the recordings in simulated scenes, a high quality sound database (wav format, 44.1 kHz sampling rate, high \textit{Signal Noise Ratio}) has been built-up from audio samples found online (\textit{freesound.org}) or with the help of an already existing sound database \cite{salamon2014dataset}. The sound database is composed of two categories of sound : the \textit{event} category, which includes 245 brief sound samples considered as salient, with a 1 to 20 seconds duration and classified among 21 sound classes (\textit{ringing bell, whistling bird, car horn, passing car, hammer, barking dog, siren, footstep, metallic noise, voice \dots}) and the \textit{background} (or \textit{texture}) category gathering 154 long duration sounds ($\approx$ 1m30), whose acoustic properties do not vary in time. This category includes among others\textit{whistling bird, crowd noise, rain, children playing in schoolyard, constant traffic noise} \dots sound classes. Each sound class is present in multiple samples (\textit{carHorn01.wav, carHorn02.wav \dots}) to bring diversity.
As the road traffic is the main component in urban environment and is the sound source of interest, recordings of car passages has been made on the Ifsttar's runway. The recordings has been made for 4 cars (Renault Senic, Renault Megane and Renault Clio, Dacia Sandero),  for different speeds and gear ratios. In all, 103 car passages have been recorded. The audio samples of the first two cars (Renault Senic and Renault Megane) are included in the \textit{SimScene}'s sound database (50 audio files totally). The last 53 audio samples are dedicated to the dictionary design as part of NMF, see section \ref{part:dictionary_building}. A full description of the recording can be found in \cite{gloaguen_creation_2017}.

@@

A non-negative matrix factorization frame has been applied as a source separation tool to estimate the traffic sound level  from a corpus of urban sound scenes artifically built. In addition, the realism of the scenes has been verified thanks to a perceptual test. The proposed protocol generate audio sample similar than the outputs of a deployed sensor networks with tha advantages of the simulation process (sound level and position of each source controlled and known).

>>>>

where $\mathbf{w}$ is a $k$ element of $\mathbf{W}$ of $F \times 1$ dimension. When $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$=1, the element $k$ from $\mathbf{W'}$ is exactly similar than in $\mathbf{W_0}$. If $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$=0, the element is fully different. Next, the similarities are sorted in descending order. The extraction of traffic elements in $\mathbf{W'}$ is carried out by a hard thresholding method \cite{donoho1994threshold}. It consists in weighting in a binary way the traffic elements $\mathbf{W'}$ according to $D_{\theta}\left(\mathbf{w_0} \Vert \mathbf{w'} \right)$ and a threshold value such as:

@@

These methods are applied on simulated sound scenes in order to compare the estimated sound levels with the exact solutions. In \cite{gloaguen2018Estimation}, the sound corpus was composed of a mix of traffic samples with specific sound classes (\textit{alert, animals, climate, human, mechanics, transportation}). Here, in order to implement this method in embedded sensors, a new more realistic sound corpus is generated based on urban recordings mixing all kind of sound sources.

@@

To transcribe the recordings in simulated scenes, a high quality sound database (wav format, 44.1 kHz sampling rate, high \textit{Signal Noise Ratio}) has been built-up from audio samples found online (\textit{freesound.org}) or with the help of an already existing sound database \cite{salamon2014dataset}. The sound database is composed of two categories of sound: the \textit{event} category, which includes 245 brief sound samples considered as salient, with a 1 to 20 seconds duration and classified among 21 sound classes (\textit{ringing bell, whistling bird, car horn, passing car, hammer, barking dog, siren, footstep, metallic noise, voice \dots}) and the \textit{background} (or \textit{texture}) category gathering 154 long duration sounds ($\approx$ 1m30), whose acoustic properties do not vary in time. This category includes among others\textit{whistling bird, crowd noise, rain, children playing in schoolyard, constant traffic noise} \dots sound classes. Each sound class is present in multiple samples (\textit{carHorn01.wav, carHorn02.wav \dots}) to bring diversity.
As the road traffic is the main component in urban environment and is the sound source of interest, recordings of car passages has been made on the Ifsttar's runway. The recordings has been made for 4 cars (Renault Senic, Renault Megane and Renault Clio, Dacia Sandero),  for different speeds and gear ratios. In all, 103 car passages have been recorded. The audio samples of the first two cars (Renault Senic and Renault Megane) are included in the \textit{SimScene}'s sound database (50 audio files totally). The last 53 audio samples are dedicated to the dictionary design as part of NMF, see section \ref{part:dictionary_building}. A full description of the recording can be found in \cite{gloaguen_creation_2017}.

@@

A non-negative matrix factorization frame has been applied as a source separation tool to estimate the traffic sound level  from a corpus of urban sound scenes artificially built. In addition, the realism of the scenes has been verified thanks to a perceptual test. The proposed protocol generate audio sample similar than the outputs of a deployed sensor networks with the advantages of the simulation process (sound level and position of each source controlled and known).
